---
title: "Effects of Covid-19 on Students"
description: |
  Examination on the stress levels experienced by students before and after Covid-19
site: distill::distill_website
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(rvest)
library(janitor)
library(plotly)
library(cowplot)


# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

```{r get-data}
semi_clean_data <- read_csv("clean_data.csv", col_types = cols(
    environment = col_character(),
    classwork_stress = col_double(),
    homework_stress = col_double(),
    homework_hours = col_double(),
    gender = col_character(),
    time_frame = col_character())) 

clean_data_expnd <- semi_clean_data %>% 
  pivot_longer(names_to = "stress_type", values_to = "stress", cols = c(homework_stress, classwork_stress)) %>% 
    mutate(time_frame_f = factor(time_frame, c("before", "after"))) %>% 
  mutate(environment = factor(environment, c("Physical","Hybrid","Virtual"))) %>% 
  mutate(gender = if_else(is.na(gender) , "NA", gender))
  
clean_data <- semi_clean_data %>% 
  mutate(time_frame_f = factor(time_frame, c("before", "after"))) %>% 
  mutate(environment = factor(environment, c("Physical","Hybrid","Virtual")))

raw_data = read_csv("responses.csv", col_types = cols(
  Category = col_character(),
  Country = col_character(),
  State = col_character(),
  Age = col_double(),
  Gender = col_character(),
  `Before-Environment` = col_character(),
  `Before-ClassworkStress` = col_double(),
  `Before-HomeworkStress` = col_double(),
  `Before-HomeworkHours` = col_double(),
  `Now-Environment` = col_character(),
  `Now-ClassworkStress` = col_double(),
  `Now-HomeworkStress` = col_double(),
  `Now-HomeworkHours` = col_double(),
  FamilyRelationships = col_double(),
  FriendRelationships = col_double())) %>% 
  clean_names()

facet_txt <- c('before' = "Before Covid-19",
               'after' = "During Covid-19",
               'homework_stress' = "Stress From Homework",
               'classwork_stress' = "Stress From Classwork",
               'Male' = "Male",
               'Female' = "Female",
               'Other' = "Other",
               'NA' = "Prefer Not To Say")

```
## Graph 1
```{r handle-data}
plot_data_stress <- clean_data_expnd %>% 
  ggplot(aes(x = stress, fill = time_frame))+
  geom_bar(show.legend = FALSE)+
  facet_wrap(~time_frame_f+stress_type, labeller = as_labeller(facet_txt), shrink = FALSE)+
  theme_bw()+
  labs(title = "Stress Levels Experienced by Students Before and During Covid-19", x = "Stress Levels", y = "Count", fill = "")

plot_data_stress
```

There was a **general increase** in stress levels for students during Covid-19. Prior to the lockdown, the average stress rating was located in the lower half of the distribution. The change resulted in a distribution that was skewed towards the higher levels. The homework stress had a higher average compared to the classwork stress both before and during Covid-19. 


This graph splits the responses up by the respondent's current learning environment to show if different environments experienced stress differently

## Graph 2

This graph splits the responses up by the respondent's current learning environment to show if different environments experienced stress differently

```{r stress-comparison, fig.height = 6}
title <- ggdraw() + draw_label("Student Stress Levels In Different Learning Environments", fontface='bold')


plot_physical <- clean_data_expnd %>% 
  filter(environment == ("Physical")) %>% 
  filter(time_frame == "after") %>% 
  ggplot(aes(x = stress))+
  geom_bar()+
  theme_bw()+
  scale_y_continuous(limits = c(0,14))+
  scale_x_continuous(limits = c(0,NA))+
  facet_wrap(~stress_type, labeller = as_labeller(facet_txt))+
  labs(x = "", y = "Count")

plot_hybrid <- clean_data_expnd %>% 
  filter(environment == ("Hybrid")) %>% 
  filter(time_frame == "after") %>% 
  ggplot(aes(x = stress))+
  geom_bar()+
  theme_bw()+
  scale_y_continuous(limits = c(0,14))+
  scale_x_continuous(limits = c(0,NA))+
  facet_wrap(~stress_type, labeller = as_labeller(facet_txt))+
  labs(x = "", y = "Count")

plot_virtual <- clean_data_expnd %>% 
  filter(environment == ("Virtual")) %>% 
  filter(time_frame == "after") %>% 
  ggplot(aes(x = stress))+
  geom_bar()+
  theme_bw()+
  scale_y_continuous(limits = c(0,14))+
  scale_x_continuous(limits = c(0,NA))+
  facet_wrap(~stress_type, labeller = as_labeller(facet_txt))+
  labs(x = "Stress Levels (0-6)", y = "Count")

plot_grid(title, plot_physical, plot_hybrid, plot_virtual,
          labels = c("","Physical", "Hybrid","Virtual"),
          vjust = -0.5,
          nrow = 4,
          rel_heights=c(0.5, 1.3, 1.3, 1.3))
```

Despite fewer data points for the hybrid and physical spaces, there are a few differences between them. Students in physical learning environments had the highest average stress level with class work.

## Graph 3

```{r}
plot_gender <- clean_data_expnd %>% 
  filter(time_frame == "after") %>% 
  ggplot(aes(x = stress))+
  geom_bar()+
  facet_wrap(~stress_type+gender, ncol = 4, labeller = as_labeller(facet_txt))+
  labs(title = "Stress Experienced by Different Genders", x = "Stress Levels", y = "Count")
plot_gender
```


```{r}

# plot_data_both <- clean_data %>% 
#   ggplot(aes(x = homework_stress, color = gender))+
#   #geom_jitter(width = 1, height = 1, aes(frame = time_frame_f))
#   geom_density(aes(frame = time_frame_f))
#   #geom_line(aes(group = paired, frame = time_frame_f), position=position_jitter(width = 0.05, height = 0.05))
#   
# plot_data_both <- ggplotly()
# plot_data_both
# 
# 
# # average_data <- raw_data %>% 
# #   mutate(x = factor(row_number())) %>% 
# #   rowwise() %>% 
# #   mutate(mymean = mean(c(before_homework_stress,now_homework_stress) )) %>% 
# #   arrange(mymean) %>% 
# #   ggplot() +
# #   geom_segment( aes(x=x, xend=x, y=before_homework_stress, yend=now_homework_stress), color="grey") +
# #   geom_point( aes(x=x, y=before_homework_stress), color=rgb(0.2,0.7,0.1,0.5), size=3 ) +
# #   geom_point( aes(x=x, y=now_homework_stress), color=rgb(0.7,0.2,0.1,0.5), size=3 ) +
# #   coord_flip()
# # average_data

# plot_data_hwk <- clean_data %>% 
#   ggplot(aes(x = homework_stress, fill = time_frame))+
#   geom_bar(show.legend = FALSE)+
#   facet_wrap(~time_frame_f, labeller = as_labeller(facet_txt))+
#   theme_bw()+
#   labs(title = "Homework Stress Levels Experienced by Students Before and During Covid-19", subtitle = "There was a general increase in homework stress during covid.\nThe distribution of stress with respect to the increase stayed roughly the same shape", x = "Stress Levels", y = "Count", fill = "")
# plot_data_clswrk <- clean_data %>% 
#   ggplot(aes(x = classwork_stress, fill = time_frame))+
#   geom_bar(show.legend = FALSE)+
#   facet_wrap(~time_frame_f, labeller = as_labeller(facet_txt))+
#   theme_bw()+
#   labs(title = "Classwork Stress Levels Experienced by Students Before and During Covid-19", subtitle = "There was an uneven increase\n in classwork stress levels, but stress levels increased as well", x = "Stress Levels", y = "Count", fill = "")
# plot_data_clswrk
# 
# 
# plot_environment <- clean_data_expnd %>% 
#   filter(time_frame == "after") %>% 
#   ggplot(aes(x = stress))+
#   geom_bar()+
#   facet_wrap(~environment+stress_type, ncol = 2)+
#   theme_bw()+
#   labs(title = "")
# plot_environment
# plot_physical

```

